Antigua-Barbuda Fish Follows August 2017

### 2019-04-22 r/Follows.Rmd

# site averages by species
sum_site_sp <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n), 
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n), 
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n), 
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n), 
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n), 
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    ) %>% 
  select(-n)

# site averages by species and phase
sum_site_sp_ph <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n), 
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n), 
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n),
    length_m = mean(length_cm),
    length_se = sd(length_cm)/sqrt(n)
    ) %>% 
  select(-n)
```

>>>>

# site averages by species
sum_site_sp <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n), 
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n), 
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n), 
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n), 
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n), 
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n)
    )

# site averages by species and phase
sum_site_sp_ph <- sum_id %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    g_frac_mean=mean(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n), 
    int_tot_mean=mean(int_tot),
    int_tot_se=sd(int_tot)/sqrt(n),
    int_scar_mean=mean(int_scar),
    int_scar_se=sd(int_scar)/sqrt(n),
    int_con_mean=mean(int_con),
    int_con_se=sd(int_con)/sqrt(n), 
    int_hetscar_mean=mean(int_hetscar),
    int_hetscar_se=sd(int_hetscar)/sqrt(n),
    int_dam_mean=mean(int_dam),
    int_dam_se=sd(int_dam)/sqrt(n),
    length_m = mean(length_cm),
    length_se = sd(length_cm)/sqrt(n)
    )

test <- sum_id %>% filter(site=="Pallaster Mid")
```
